---
title: Letter to the Editor
author: "Not just for programmers: A friendly guide on the benefits of GitHub for accelerating collaborative research in Ecology and Evolution"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: cosmo 
    highlight: tango
    self_contained: true
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina = 2)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(hrbrthemes)
library(tidyverse)

update_geom_font_defaults(font_rc)
```

Dear Editor,

We would like to submit our manuscript entitled “Not just for programmers: A friendly guide on the versatility of GitHub for accelerating collaborative research in Ecology and Evolution” for consideration to be published in OUR_CHOICE_OF_JOURNAL. 
Our study provides researchers in ecology and evolution with a critical review on thirteen practical ways they can use Github -- an online, cloud-based service for cooperative and documented code development -- to make their research more collaborative, transparent, and reproducible.

Scientific advancement fundamentally requires researchers to adopt reproducible, collaborative and transparent practices.

Most scientists, including ecologists and evolutionary biologists, have become critically dependent on computational tools in their research.
This code-dependent workflow imposes steep requirements towards an efficient, well-documented process in the publication and collaboration of maintainable scientific code.
Albeit, many researchers lack exposure to adequate software development practices and thus are required to dedicate valuable time and effort to self-teach the use of research-facilitating tools, and thus may find practical barriers when applying adequate standards to maintain their scientific code.
In our study, we review and discuss one of the most used web-based platforms for computational version control and collaboration, GitHub, and provide researchers in ecology and evolutionary biology with practical workflows aimed at facilitating their scientific code and management process.

*Include another paragraph describing the implications of the study.*

The enclosed manuscript has not been previously published and is not under consideration for publication in another journal or book. 
All authors have contributed and reviewed the current version of the manuscript and agreed to its submission to OUR_CHOICE_OF_JOURNAL.

We appreciate your time and consideration of our manuscript for publication in your journal.

Sincerely,

OUR_CORRESPONDING AUTHOR, on behalf of all co-authors

