---
title: "Figure: the scatterblob"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goal: This is a summary figure, e.g., "here are all the ways and here are the entry points with low technical difficulty, and some  for beginner s and the more advanced ways to use it".
There are ways to use github that allows different degrees of collaboration that do not require too many technical skills.

Use even notation across text and figure

space out middle blobs
labels to x and y axis
homogenizing titles of ways to use github

## The data

Data for this figure was generated on a collaborative [google spread sheet](https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit#gid=0). Cognitive load [was measured in a different file](https://docs.google.com/spreadsheets/d/1OLBR3M0uV3PMSazWUYHgPeX28wllAgS4PIlJXaNu-2o/edit#gid=0). 

Reading the data csv file:

```{r}
library(readr)
scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

View(scatterblob_data)

```

Creating the `my_data` object from :

```{r}
names(scatterblob_data)
scatterblob_data$x1 <- scatterblob_data$`Degree of immediate collaborativeness X1`
scatterblob_data$x2 <- scatterblob_data$`Degree of immediate collaborativeness X2`
scatterblob_data$y <- scatterblob_data$`Cognitive load absolute`

my_data <- scatterblob_data[,c("Ways to use GitHub","y", "x1", "x2")]
my_data
```


## Plotting the data


### First try

Using original cognitive values.

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_0.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5), 
     y = c(1.75, 9.75), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = 0.5, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10), 
     cex = 0.7,
     adj = 1,
     labels = c("Elementary", 
                "Low \nintermediate", 
                "Intermediate", 
                "Pre- \nAdvanced", 
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = scatterblob_data$`Cognitive load`, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)


### Second try

Distributing cognitive load evenly:

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_1.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
plot(x = c(0.5, 5.5), 
     y = c(0.5, 14), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre-\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre-\nAdvanced", 
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```




![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob_1.pdf)

